\documentclass[10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{hyperref}

\newcommand{\vitem}{\vspace*{-.4pc}\item}
% \newcommand*{\vsection}{1}{\vspace*{-1pc}\section*{\centering \#1}\vspace*{-.5pc}}

\begin{document}
\begin{tabular}{lcr}
  \textbf{Permanent Address}&&\textbf{Contact info}\\
  \href{}{}&\hspace*{2cm}\huge{Cesar Romero}\hspace*{2cm}&\href{mailto:cesar@romero.ws}{\texttt{cesar@romero.ws}}\\
Seattle, WA
98133&\href{http://cesar.romero.ws}{http://cesar.romero.ws}&$+1-773-4130610$\\
\end{tabular}\\
\underline{\makebox[\textwidth]{\hfill}}
\begin{quote}
  \centering{}
 \textbf{Education}
\end{quote}
\href{http://www.ucla.edu}{\textbf{University of California, Los Angeles}}\\
Master of Science in Computer Science. GPA: $3.84$\hfill June 2010
Coursework Includes: Automated Reasoning, Approximation Algorithms,
Heuristic Search, Game Theory, Natural Language Processing, Cognitive
Systems (Causality), Probabilistic Reasoning and Machine Learning.

\noindent\href{http://www.usb.ve}{\textbf{Universidad Simon Bolivar, Caracas, Venezuela}}\\
Computer Engineer. GPA: $3.45$\hfill November 2007

\centering{}\textbf{Work Experience.}
\flushleft{\textbf{Software Development Engineer II.}} Amazon.com \hfill June 2011 - present
\begin{itemize}
  \vitem China Global Store launch team. Designed the checkout
  experience for users on the chinese website buying items to be
  fulfilled from fullfillment centers in north america.
  \vitem Delivery date search launch team. Designed and developed a
  system to classify items according to the transportation
  capabilities of carriers and fed these into a search index to help
  power the filter on Amazon.com's home page.
  \vitem Developed and maintained an automated system to review
  potentially hazardous items in the Amazon catalog; it controlled the
  flow of $\sim$1M catalog items every week according to flexible rules to
  meet business requirements.
  \vitem Maintained a rule-based classification system with
  self-service tools to help business users detect prohibited products
  by periodically scanning items recently added to the catalog using Hadoop.
\end{itemize}

\flushleft{\textbf{Software Engineer Intern.}} Google Inc. \hfill Summer 2010
\begin{itemize}
  \vitem Designed and developed a DHCP server for the Data Centers to
  netboot production devices as part of an automated installation
  process.
\end{itemize}

\flushleft{\textbf{Software Engineer.}} UCLA - Computer Science
Department. \hfill Spring 2010
\begin{itemize}
  \vitem Deployed an internal system to manage student resumes and select job postings using \href{http://drupal.org/}{Drupal} 6 and MySQL on Linux (\href{http://www.centos.org/}{CentOS} 5.5)
\end{itemize}

% \flushleft{\textbf{Teaching Assistant.}} University of California, Los
% Angeles -- UCLA. \hfill September 2009 - June 2010\\
% Led and prepared weekly discussion sessions for the School of
% Engineering focused on Engineering ethics and technical
% writing. Hired for the academic year 2009-2010.

\flushleft\textbf{Software and Web Developer.} Universidad Simón Bolívar, Caracas, Venezuela

\textbf{Remote Sensors Lab}. \hfill October 2007 - June 2008
\begin{itemize}
  \vitem Designed and developed a novel algorithm and its
  \href{http://ood.cbm.usb.ve/surgencia/sst_modis/mostrar_imagen?img=66}{web
    interface}; it uses information extracted from satellite images to
  compute the area of different
  \href{http://en.wikipedia.org/wiki/Upwelling}{upwelling} systems.

  \vitem Implemented
  \href{http://ood.intecmar.usb.ve/surgencia/sst_modis/}{web
    applications} to view metadata extracted from satellite images and
  integrate other tools that were previously developed at the
  Institute; used Python, JavaScript and MySQL with the
  \href{http://turbogears.org/}{TurboGears} framework.

\vitem Developed a completely automated process that
  downloads, transforms and inserts the satellite images into the
  databases for later use by the web applications. Used Python and bash.
\end{itemize}

\textbf{System and Network Administrator.} Universidad Simón Bolívar, Caracas, Venezuela

\textbf{Remote Sensors Lab}\hfill October 2007 - June 2008
\begin{itemize}
\vitem Migrated a running MySQL and Apache server across different
  linux distributions (Gentoo \& \href{http://www.archlinux.org/}{Arch}).
\end{itemize}

\noindent\textbf{Natural Resources Institute} \hfill October 2006 - June 2008
\begin{itemize}
\vitem Mantained a small network with 7 windows clients, 2 printers, 1
  linux server. Installed and configured various network services including:
  Apache, Subversion, Bind, Postfix
\end{itemize}

\noindent\textbf{Computer Science Department} \hfill January 2004 -
  July 2006.
\begin{itemize}
\vitem Worked in a group of 10-15 students in the administration of the
  \href{http://www.ldc.usb.ve}{Computer Science Department network}
  at Universidad Simón Bolívar. 50+ windows and linux clients, 3+
  printers, 5+ linux servers including: DHCP, Apache, Samba, DNS,
  LDAP, NFS. Supervised a daily backup system and user accounts.
\end{itemize}

\noindent\textbf{Artificial Intelligence Group}\hfill September 2006 - October 2007
\begin{itemize}
  \vitem Administered the \href{http://www.gia.usb.ve}{Artificial
    Inteligence Group} Lab. 7+ linux clients and 2 linux
  servers. Created custom \href{http://www.archlinux.org/}{Arch Linux}
  packages to suit the necessity of the lab, packages include: Apache
  and \LaTeXe{}
\end{itemize}

\centering{\textbf{Skills}}
\flushleft\textbf{Programming Languages :} Python, javascript, Java,
C++, C; Basic PHP, Perl.

\noindent\textbf{Natural Languages :} Native Spanish, fluent English
and intermediate German.

\vspace{1pc}\centering{\textbf{Projects}}
\flushleft\textbf{Large Scale Parallel Breath-First Search}
\begin{itemize}
  \vitem Developed a multi-threaded external search algorithm in C
  that read and wrote up to 2TB of data to disk. Configured hardware and
  software RAID testing different filesystems on internal and external
  disks on Linux to run the algorithm and measure its
  performance. Related work presented at a Search workshop in AAAI-08
  \hfill 2007
\end{itemize}

\textbf{TERA - Emergency Web Application}
\begin{itemize}
\item Led a team to design and develop a web application to help
  manage resources in emergency situations and natural disasters,
  handling users, groups and an internal message system. Worked in a
  group of 10 (4 developers) for a period of twelve weeks. Written
  using PHP, \href{www.smarty.net/}{Smarty},
  \href{pear.php.net/package/DB}{Pear DB} and MySQL.
\end{itemize}

% \textbf{Don Gustavo Inc.} \href{http://www.dongustavos.com}{www.dongustavos.com}\hfill 2009
% \begin{itemize}
%   \vitem Designed and maintain the website.  Set up Content Management
%   System (CMS) Joomla!, MySQL database. User accounts for email and
%   website update purposes.
% \end{itemize}

\textbf{Computer Graphics}\hfill Fall 2006
\begin{itemize}
 \vitem Implemented the global illumination algorithm
  \href{http://en.wikipedia.org/wiki/Radiosity_\%283D_computer_graphics\%29}{``radiosity''}
  and reproduced the
  \href{http://en.wikipedia.org/wiki/Cornell_box}{Cornell Box}.
  Created a 3D game of marbles on a terrain modified by the user and a
  2D implementation of
  \href{http://en.wikipedia.org/wiki/Breakout_\%28arcade_game\%29}{``breakout''}
  using OpenGL
\end{itemize}

\centering{\textbf{Interests}}
\flushleft{}\textbf{Hackathons}
\begin{itemize}
\vitem Participated in several Amazon internal hackathons including:
transportation hack 2011, social hack 2011, visualization hack 2012,
personalization challenge 2012, social hack 2012 (won most innovative
award), search \& discovery hack 2013, amazon local hack 2013 (second
place), machine learning hack 2014.
\vitem Participated in some civic hacking: Hack to end homelesness 2013,
code for seattle 2014.
\end{itemize}

\flushleft{}\textbf{Programming Competitions}
\begin{itemize}
\vitem Participated in local and national ACM programming competitions, obtained 5th and 4th place in 2006 and 2007 respectively
\vitem Enjoy online programming competitions such as TopCoder, Google
Codejam, Project Euler and Facebook Hackercup.
\end{itemize}

\textbf{Robotics Competitions}
\begin{itemize}
\vitem Participated in IEEE 2006 robotics competition. Obtained 2nd place in the national and 6th place in the Latin American competition in the LEGO category.
\end{itemize}

\centering{\textbf{Publication}}
\begin{itemize}
\vitem Cesar Romero, Julio Castillo and
\href{http://www.ldc.usb.ve/~bonet}{Blai Bonet}. 2008. Multiple
Symmetries in Sliding-Tile Puzzle: First Experiments. \emph{Proceedings of the First International Symposium on Search Techniques in Artificial Intelligence and Robotics (STAIR-2008)}. Chicago, Illinois. July 2008.
\end{itemize}

\centering{\textbf{References}}
\begin{itemize}
\vitem Contact me for personal references.
\end{itemize}
\end{document}
